Novelty Detection for Visual Place Classification

### 2011-07-13 pdis/presentation2/cold-database-sample.tex
Fixed scons rule for PDIS/presentation2

\begin{figure}
\begin{center}
\includegraphics[width=0.15\textwidth]{cold/Saarbruecken_CR}
\includegraphics[width=0.15\textwidth]{cold/Saarbruecken_TR}
\includegraphics[width=0.15\textwidth]{cold/Freiburg_PA}
\includegraphics[width=0.15\textwidth]{cold/Freiburg_LO}
\includegraphics[width=0.15\textwidth]{cold/Ljubljana_LAB}
\includegraphics[width=0.15\textwidth]{cold/Ljubljana_2PO}

\includegraphics[width=0.15\textwidth]{cold/Saarbruecken_RL}
\includegraphics[width=0.15\textwidth]{cold/Saarbruecken_PA}
\includegraphics[width=0.15\textwidth]{cold/Freiburg_1PO}
\includegraphics[width=0.15\textwidth]{cold/Freiburg_TL}
\includegraphics[width=0.15\textwidth]{cold/Ljubljana_CR}
\includegraphics[width=0.15\textwidth]{cold/Ljubljana_PA}

\includegraphics[width=0.15\textwidth]{cold/Saarbruecken_CR(1)}
\includegraphics[width=0.15\textwidth]{cold/Saarbruecken_TR(1)}
\includegraphics[width=0.15\textwidth]{cold/Freiburg_1PO(1)}
\includegraphics[width=0.15\textwidth]{cold/Freiburg_TL(1)}
\includegraphics[width=0.15\textwidth]{cold/Ljubljana_LAB(1)}
\includegraphics[width=0.15\textwidth]{cold/Ljubljana_PA(1)}
\end{center}
\caption{Sample data from the COLD database. Images were acquired from three diferent indoor laboratory enviroments located in diferent European cities: Saarbrücken, Freiburg and Ljubjlana.}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.15\textwidth]{figures/cold/Saarbruecken_CR.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Saarbruecken_TR.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Freiburg_PA.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Freiburg_LO.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Ljubljana_LAB.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Ljubljana_2PO.jpg}

\includegraphics[width=0.15\textwidth]{figures/cold/Saarbruecken_RL.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Saarbruecken_PA.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Freiburg_1PO.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Freiburg_TL.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Ljubljana_CR.jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Ljubljana_PA.jpg}

\includegraphics[width=0.15\textwidth]{figures/cold/Saarbruecken_CR(1).jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Saarbruecken_TR(1).jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Freiburg_1PO(1).jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Freiburg_TL(1).jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Ljubljana_LAB(1).jpg}
\includegraphics[width=0.15\textwidth]{figures/cold/Ljubljana_PA(1).jpg}
\end{center}
\caption{Sample data from the COLD database. Images were acquired from three diferent indoor laboratory enviroments located in diferent European cities: Saarbrücken, Freiburg and Ljubjlana.}
\end{figure}

### 2011-07-13 pdis/presentation2/presentation.tex
Fixed scons rule for PDIS/presentation2

\documentclass[compress]{beamer}
\usepackage[utf8x]{inputenc}
\usepackage{default}
\usepackage{graphics}
\useinnertheme{rounded}
\usecolortheme{whale}
\useoutertheme[subsection=false]{miniframes}
\graphicspath{{figures/}}

@@

\section{Problem Definition and Motivation}
\subsection{Place Classification}
\begin{frame}{Place Classification}
\begin{figure}
\includegraphics[width=0.75\textwidth]{place_classification}
\end{figure}
Mapping of robot location to concepts:
\begin{itemize}
\item Improves human interaction.
\item High-level and robust localization information.
\item Knowledge about room categories and their properties.
\item Context-aware decisions\cite{dey2000towards}.
\end{itemize}
\end{frame}

\subsection{Novelty Detection}
\begin{frame}{Novelty Detection}
\begin{figure}
\includegraphics[width=0.75\textwidth]{novelty_detection}
\end{figure}

@@

\begin{columns}[t]
    \column{.5\textwidth}
    \begin{figure}
        \includegraphics[width=.9\textwidth]{classification.pdf}
    \end{figure}
    \begin{quote}This is harder than the classification problem\cite{cortes1995support}\end{quote}.
    \column{.5\textwidth}
    Several approaches\cite{bishop2006pattern}:
    \begin{itemize}
        \item Nearest Neighbour
        \item Neural Networks
        \item Gaussian Mixture Models
        \item several others and extensions\dots 
    \end{itemize}
\end{columns}
\end{frame}

\begin{frame}{Classification}
\framesubtitle{Support Vector Machines}
    \begin{columns}[t]
    \column{.5\textwidth}
    \begin{figure}
        \includegraphics[width=.75\textwidth]{Svm_max_sep_hyperplane_with_margin}
    \end{figure}
        SVM uses a max-margin hyperplane to separate two classes.
    \column{.5\textwidth}
    \begin{block}{Kernel-Trick}
        Can be extended to non-linear classification:\\
        $K(x, y) = \phi(x)\cdot\phi(y)$
    \end{block}
    \begin{block}{Multi-class}
        Can be used in multi-class scenarios:
        \begin{itemize}
            \item One-Versus-One
            \item One-Versus-All
        \end{itemize}
    \end{block}
    \end{columns}
\end{frame}

@@

    \column{.5\textwidth}
    \begin{figure}
        \includegraphics[width=\textwidth]{sift/sift}
        \caption{SIFT and other local features have been proven useful in object detection.}
    \end{figure}
    \column{.5\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth]{crfh_model}
    \caption{Composed Receptive Field Histograms can be used to extract appearance.}
    \end{figure}
    \end{columns}
\end{frame}

\begin{frame}{Features}
\framesubtitle{Others\dots}
    \begin{figure}
    \includegraphics[width=0.60\textwidth]{laser_and_depth_input}
    \caption{Lasers can be used to extract useful features.}
    \end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Novelty Detection}
\begin{frame}{Novelty Detection}
\framesubtitle{Probability}
    \begin{figure}
        \includegraphics[width=0.75\textwidth]{novelty.pdf}
    \end{figure}
    Novelty detection can be modeled by calculating the probability of a given input being generated and triggering on that value\cite{bishop1994novelty}.
\end{frame}

\begin{frame}{Novelty Detection}
\framesubtitle{Kernel PCA}
    \begin{columns}[t]
    \column{.5\textwidth}
        \begin{itemize}
        \item Principal Component Analysis
        \item Extended for non-linear (kernel-trick)
        \item Radial Basis Function Kernel
        \item Use reconstruction error as novelty measure
        \item Good results on several applications
        \end{itemize}
    \column{.5\textwidth}
    \begin{figure}
        \includegraphics[width=0.9\textwidth]{ringlinesquare_kpca}
    \end{figure}
        Kernel PCA used on a strange shaped class\cite{Hoffmann2007863}.
    \end{columns}
\end{frame}

@@

\begin{frame}{Graphical Models}
    \begin{itemize}
        \item Represent a system of random variables
        \item Allow to model conditional independence
        \item Act as a filter of probability distributions
        \item Can calculate joint probabilities (inference).
    \end{itemize}
    \begin{columns}[t]
    \column{0.3\textwidth}
        \begin{figure}
            \includegraphics[width=0.5\textwidth]{graphical-models/BayesNet.pdf}
            \caption{Bayes Networks}
        \end{figure}
    \column{0.3\textwidth}
        \begin{figure}
            \includegraphics[width=0.5\textwidth]{graphical-models/MarkovRandomField}
            \caption{Markov Random Field}
        \end{figure}
    \column{0.3\textwidth}
        \begin{figure}
            \includegraphics[width=0.60\textwidth]{graphical-models/FactorGraph.pdf}
            \caption{Factor Graph}
        \end{figure}
    \end{columns}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Approach}
\subsection{Layers}
\begin{frame}{Layers}
    \begin{figure}
        \includegraphics[width=0.65\textwidth]{system-representation/layers.pdf}
    \end{figure}
\end{frame}

\begin{frame}{Layers}
\framesubtitle{Conceptual Graph}
    \begin{figure}
        \includegraphics[width=\textwidth]{system-representation/graph.pdf}
    \end{figure}
\end{frame}

\begin{frame}{Layers}
\framesubtitle{Novelty Detection}
    \begin{figure}
        \includegraphics[width=\textwidth]{system-representation/novelty-detection.pdf}
    \end{figure}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Plan}
\begin{frame}{Work Plan}
\begin{figure}
\includegraphics[width=\textwidth]{gantt.pdf}
\end{figure}

>>>>

\documentclass[compress]{beamer}
\usepackage[utf8x]{inputenc}
\usepackage{default}
\usepackage{graphics}
\useinnertheme{rounded}
\usecolortheme{whale}
\useoutertheme[subsection=false]{miniframes}

@@

\section{Problem Definition and Motivation}
\subsection{Place Classification}
\begin{frame}{Place Classification}
\begin{figure}
\includegraphics[width=0.75\textwidth]{figures/place_classification.png}
\end{figure}
Mapping of robot location to concepts:
\begin{itemize}
\item Improves human interaction.
\item High-level and robust localization information.
\item Knowledge about room categories and their properties.
\item Context-aware decisions\cite{dey2000towards}.
\end{itemize}
\end{frame}

\subsection{Novelty Detection}
\begin{frame}{Novelty Detection}
\begin{figure}
\includegraphics[width=0.75\textwidth]{figures/novelty_detection.png}
\end{figure}

@@

\begin{columns}[t]
    \column{.5\textwidth}
    \begin{figure}
        \includegraphics[width=.9\textwidth]{figures/classification.pdf}
    \end{figure}
    \begin{quote}This is harder than the classification problem\cite{cortes1995support}\end{quote}.
    \column{.5\textwidth}
    Several approaches\cite{bishop2006pattern}:
    \begin{itemize}
        \item Nearest Neighbour
        \item Neural Networks
        \item Gaussian Mixture Models
        \item several others and extensions\dots 
    \end{itemize}
\end{columns}
\end{frame}

\begin{frame}{Classification}
\framesubtitle{Support Vector Machines}
    \begin{columns}[t]
    \column{.5\textwidth}
    \begin{figure}
        \includegraphics[width=.75\textwidth]{figures/Svm_max_sep_hyperplane_with_margin.png}
    \end{figure}
        SVM uses a max-margin hyperplane to separate two classes.
    \column{.5\textwidth}
    \begin{block}{Kernel-Trick}
        Can be extended to non-linear classification:\\
        $K(x, y) = \phi(x)\cdot\phi(y)$
    \end{block}
    \begin{block}{Multi-class}
        Can be used in multi-class scenarios:
        \begin{itemize}
            \item One-Versus-One
            \item One-Versus-All
        \end{itemize}
    \end{block}
    \end{columns}
\end{frame}

@@

    \column{.5\textwidth}
    \begin{figure}
        \includegraphics[width=\textwidth]{figures/sift/sift.pdf}
        \caption{SIFT and other local features have been proven useful in object detection.}
    \end{figure}
    \column{.5\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth]{figures/crfh_model.jpg}
    \caption{Composed Receptive Field Histograms can be used to extract appearance.}
    \end{figure}
    \end{columns}
\end{frame}

\begin{frame}{Features}
\framesubtitle{Others\dots}
    \begin{figure}
    \includegraphics[width=0.60\textwidth]{figures/laser_and_depth_input.pdf}
    \caption{Lasers can be used to extract useful features.}
    \end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Novelty Detection}
\begin{frame}{Novelty Detection}
\framesubtitle{Probability}
    \begin{figure}
        \includegraphics[width=0.75\textwidth]{figures/novelty.pdf}
    \end{figure}
    Novelty detection can be modeled by calculating the probability of a given input being generated and triggering on that value\cite{bishop1994novelty}.
\end{frame}

\begin{frame}{Novelty Detection}
\framesubtitle{Kernel PCA}
    \begin{columns}[t]
    \column{.5\textwidth}
        \begin{itemize}
        \item Principal Component Analysis
        \item Extended for non-linear (kernel-trick)
        \item Radial Basis Function Kernel
        \item Use reconstruction error as novelty measure
        \item Good results on several applications
        \end{itemize}
    \column{.5\textwidth}
    \begin{figure}
        \includegraphics[width=0.9\textwidth]{figures/ringlinesquare_kpca.jpg}
    \end{figure}
        Kernel PCA used on a strange shaped class\cite{Hoffmann2007863}.
    \end{columns}
\end{frame}

@@

\begin{frame}{Graphical Models}
    \begin{itemize}
        \item Represent a system of random variables
        \item Allow to model conditional independence
        \item Act as a filter of probability distributions
        \item Can calculate joint probabilities (inference).
    \end{itemize}
    \begin{columns}[t]
    \column{0.3\textwidth}
        \begin{figure}
            \includegraphics[width=0.5\textwidth]{figures/graphical-models/BayesNet.pdf}
            \caption{Bayes Networks}
        \end{figure}
    \column{0.3\textwidth}
        \begin{figure}
            \includegraphics[width=0.5\textwidth]{figures/graphical-models/MarkovRandomField}
            \caption{Markov Random Field}
        \end{figure}
    \column{0.3\textwidth}
        \begin{figure}
            \includegraphics[width=0.60\textwidth]{figures/graphical-models/FactorGraph.pdf}
            \caption{Factor Graph}
        \end{figure}
    \end{columns}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Approach}
\subsection{Layers}
\begin{frame}{Layers}
    \begin{figure}
        \includegraphics[width=0.65\textwidth]{figures/system-representation/layers.pdf}
    \end{figure}
\end{frame}

\begin{frame}{Layers}
\framesubtitle{Conceptual Graph}
    \begin{figure}
        \includegraphics[width=\textwidth]{figures/system-representation/graph.pdf}
    \end{figure}
\end{frame}

\begin{frame}{Layers}
\framesubtitle{Novelty Detection}
    \begin{figure}
        \includegraphics[width=\textwidth]{figures/system-representation/novelty-detection.pdf}
    \end{figure}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Plan}
\begin{frame}{Work Plan}
\begin{figure}
\includegraphics[width=\textwidth]{figures/gantt.pdf}
\end{figure}
